### 2020-07-28 draft.Rmd
Add paragraph about quantile regression

todo(aaron): address quantile regression

>>>>

The authors also estimate quantile regressions at the 10th through 90th deciles. The estimated effects are significant after 12 months when comparing the commitment-saving group with the full control group. The statistical and practical significance disappears when comparing the commitment-savings group with the marketing group.
